<!--
  %\VignetteIndexEntry{Use the Two-column Docco Style}
  %\VignetteEngine{knitr::docco_classic_notangle}
  %\VignetteEncoding{UTF-8}
-->

# Use the Two-column Docco Style

The two-column [Docco](https://github.com/jashkenas/docco) style is one of my favorite HTML layouts for R Markdown (v1) output. You can use the vignette engine `knitr::docco_classic`, or the function `knitr::rocco()` to compile an R Markdown document to HTML using this style. The main feature of this layout is that it arranges text in the left column, and code in the right column.

# Setup

Just like the vignette [LP-demo1](LP-demo1.html), we set up some **knitr** chunk options first.

```{r setup, purl=FALSE}
knitr::opts_chunk$set(eval = FALSE, tidy = FALSE)
```

# A Markdown Generator

First we create a list `md` with a few function members to generate raw Markdown output.

```{r}
#' A Markdown generator
#' 
#' You can generate Markdown text using the function elements of this object.
#' @return Each function element returns a character vector.
#' @export
#' @examples md$b('bold'); md$em('emphasize'); md$ul(head(letters))
md = local({
```

I'm using `local()` here because I want to create a local function `enclose()` below, which wraps its argument `x` by a character string `by`:

```{r}
  enclose = function(x, by = '') paste0(by, x, by)
```

Then `md` is basically a list of members `b` (**bold**), `em` (_emphasize_), `code`, `link`, `ol` (ordered list), and `ul` (unordered list):

```{r}
  list(
       b = function(x) enclose(x, '**'),
      em = function(x) enclose(x, '_'),
    code = function(x) enclose(x, '`'),
    link = function(href, text) sprintf('[%s](%s)', text, href),
      ol = function(x) sprintf('1. %s\n', x),
      ul = function(x) sprintf('- %s\n', x)
  )
})
```

# Examples

Now we show some text output, including plain R console output as well as Markdown output.

```{r eval=TRUE, purl=FALSE}
1 + 1
10:1 + 10
dnorm(0)
```

For raw Markdown output, you need the chunk option `results = 'asis'`.

```{r eval=TRUE, purl=FALSE, results='asis'}
library(rlp)
cat(
  'Show some raw Markdown content here. ',
  'This is ', md$b('bold'), ' and ', md$em('emphasized'), '. ',
  'Also a code fragment ', md$code('fivenum(1:10)'), '. ',
  'A link to ', md$link('http://www.r-project.org', 'R homepage'), '. ',
  '\n\n',
  'An ordered list:\n\n', md$ol(head(letters)),
  '\n\n',
  'An unordered list:\n\n', md$ul(head(LETTERS)),
  sep = ''
)
```

You can display a table as well.

```{r eval=TRUE, purl=FALSE}
knitr::kable(head(iris))
```
